---
title: The Question
author: ''
date: '2021-11-15'
slug: []
categories: []
tags: []
weight: 3
---

Let's take a closer look at the data collected *with*  time pressure.

Is there a difference between the decision times of the male and female participants under pressure? 

```{r, echo = FALSE, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(haven)
library(here)
library(knitr)
library(kableExtra)

library(tidyverse)
```

```{r}
RTPWA<-read_dta(here("content/basics/Data/Replication_WebAppendix.dta"))
SampleDat<-RTPWA%>%select(female, TimeNTP)%>%
              mutate(female = as_factor(female))

SampleDat2<-RTPWA%>%select(female, TimeTP)%>%
              mutate(female = as_factor(female))



ggplot(data = SampleDat2, aes(TimeTP,group = female,fill = female))+
          geom_histogram( alpha = 0.6)+
          scale_fill_viridis_d()+
          xlab("Seconds to Decide")+
          #coord_cartesian(xlim = c(min(data$TimeTP, data$TimeNTP), max(data$TimeTP, data$TimeNTP)))+
          theme_bw()+
          ggtitle("Decision Times: With Time Pressure")
```

If we look at the average decision times for males and females, we get and idea of the central tendency.

```{r}
SampleDat2%>%
  group_by(female)%>%
  summarise('Average Decision Time' = mean(TimeTP))%>%
  kable(caption="Average decision times for males and females", digits = 2)%>%
  kable_styling(bootstrap_options="striped", full_width = F)
```

If we just look at the averages, we might be tempted to say that they are different. But the averages alone do not take into account the way that the data are *distributed*, so we don't really know *how* different.


To decide whether or not these averages are different, one technique is the classic 'Student's t-test,' which we will explore on the next page.

