---
title: t-test 4
author: ''
date: '2021-11-17'
slug: []
categories: []
tags: []
weight: 9
---

```{r, echo = FALSE, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(haven)
library(here)
library(knitr)
library(kableExtra)

library(tidyverse)
```

```{r, echo = F}
RTPWA<-read_dta(here("content/basics/Data/Replication_WebAppendix.dta"))
SampleDat<-RTPWA%>%select(female, TimeNTP)%>%
              mutate(female = as_factor(female))

SampleDat2<-RTPWA%>%select(female, TimeTP)%>%
              mutate(female = as_factor(female))


# t.test(SampleDat[SampleDat$female==0,]$TimeNTP, SampleDat[SampleDat$female==1,]$TimeNTP)

v.testTP<-var.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP)

t.testTP<-t.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP, 
                 var.equal = TRUE)
```

## What is the t-test doing? 

The t-test is based on the notion that we have a *sample* from a *population*. 

- the size of that sample in our case is $n = n_m + n_f$
- The t-test statistic takes our sample data and provides us with a number.
$$
t = \frac{\hat{\mu}_m - \hat{\mu}_f}{\sqrt{\frac{(n_m - 1)\hat{\sigma}_m^2 + (n_f -1)\hat{\sigma}^2_f}{n_m+n_f-2}}} = `r t.testTP$statistic`
$$

- If we were to take *another* sample of the *same size* ($n$) from that same population, and calculate the t-statistic for that new sample, we would get a *different* number for $t$.







