---
title: t-test 6
author: ''
date: '2021-11-17'
slug: []
categories: []
tags: []
weight: 11
---

Should we reject the null hypothesis that the population average decision times with time pressure are the same for males and females?

The t-test permits us to ask the a specific question: **If the null hypothesis is true, what is the probability of observing a value the same, or more extreme, than the test statistic that we observed in our sample?**

If this probability is *low* we will *reject the null hypothesis*: we will essentially decide that this observed statistic is different enough that we would not attribute this difference to sampling error alone.

Now, because the t-distribution is a probability distribution, the total *area below the t-distribution* is 1.

So we need to decide what *level of significance* we are comfortable with first, and then we can determine the probability that our observed test statistic could be as extreme or more so that what we just observed.





For a two-tailed test (i.e. our alternative hypothesis is $\neq$ to some value), the $p$-value of our test statistic is twice the area towards the nearest *tail*.

```{r, echo = FALSE, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(haven)
library(here)
library(knitr)
library(kableExtra)

library(tidyverse)
library(plotly)
library(htmlwidgets)
```

```{r, echo = F}
RTPWA<-read_dta(here("content/basics/Data/Replication_WebAppendix.dta"))
SampleDat<-RTPWA%>%select(female, TimeNTP)%>%
              mutate(female = as_factor(female))

SampleDat2<-RTPWA%>%select(female, TimeTP)%>%
              mutate(female = as_factor(female))


# t.test(SampleDat[SampleDat$female==0,]$TimeNTP, SampleDat[SampleDat$female==1,]$TimeNTP)

v.testTP<-var.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP)

t.testTP<-t.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP, 
                 var.equal = TRUE)

# tail area tot he right of t statistic
1-pt(t.testTP$statistic, df = t.testTP$parameter)

# p-value (2 times the tail area)
2*(1-pt(t.testTP$statistic, df = t.testTP$parameter))

# confirm

t.testTP
```


