---
title: t-test 3
author: ''
date: '2021-11-15'
slug: []
categories: []
tags: []
weight: 8
---

The t-test statistic combines elements from our sample: our sample means ($\hat{\mu}_m$, $\hat{\mu}_f$), the standard deviations, and the number of observations in each sample. 

In this case the test statistic is the ratio of the difference in our sample means to the square root of the sum of the standard deviations for each sample.

$$
t = \frac{\hat{\mu}_m - \hat{\mu}_f}{\sqrt{\frac{(n_m - 1)\hat{\sigma}_m^2 + (n_f -1)\hat{\sigma}^2_f}{n_m+n_f-2}}}
$$

```{r, echo = FALSE, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(haven)
library(here)
library(knitr)
library(kableExtra)

library(tidyverse)
```

```{r, echo = F}
RTPWA<-read_dta(here("content/basics/Data/Replication_WebAppendix.dta"))
SampleDat<-RTPWA%>%select(female, TimeNTP)%>%
              mutate(female = as_factor(female))

SampleDat2<-RTPWA%>%select(female, TimeTP)%>%
              mutate(female = as_factor(female))


# t.test(SampleDat[SampleDat$female==0,]$TimeNTP, SampleDat[SampleDat$female==1,]$TimeNTP)

v.testTP<-var.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP)

t.testTP<-t.test(SampleDat2[SampleDat2$female==0,]$TimeTP, SampleDat2[SampleDat2$female==1,]$TimeTP, 
                 var.equal = TRUE)
```


There are other variations to this t-test^[This particular t-test takes as given that the variance in decisions are the same for males and females. We have evidence to support the assumption of equal variance this in this case ($p$- value of an F-test `r v.testTP$p.value`). ]. 
